Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-07-01 Manuscript/HI_Model_ms.Rmd
re-organized directory structure

## Abstract

The State of Hawai`i recently passed legislation setting a goal to be carbon neutral by 2045. Meeting this goal will partly depend on carbon sequestration by terrestrial ecosystems, yet the future direction and magnitude of the land carbon sink in the Hawaiian Islands is highly uncertain. We used simulation modeling to assess how projected future changes in climate and land use will influence ecosystem carbon balance in the Hawaiian Islands under four unique scenarios over a 90-year timespan. Net ecosystem carbon balance declined under all four scenarios. Moving from a high to a low radiative forcing scenario reduced net ecosystem carbon loss by ~21%, and net carbon losses were reduced by a total of ~55% under the combined scenario of low radiative forcing and low rates of land‐use change. A sensitivity test of the CO~2~ fertilization effect on plant productivity revealed it to be a major source of uncertainty in projections of ecosystem carbon balance. Reconciling this uncertainty in how net photosynthesis will respond to rising atmospheric CO~2~ will be essential to better constrainment of models used to evaluate the effectiveness of ecosystem‐based climate mitigation strategies.

@@

## Methods

>>>>

## Abstract
The State of Hawai`i recently passed legislation setting a goal to be carbon neutral by 2045. Meeting this goal will partly depend on carbon sequestration by terrestrial ecosystems, yet the future direction and magnitude of the land carbon sink in the Hawaiian Islands is highly uncertain. We used simulation modeling to assess how projected future changes in climate and land use will influence ecosystem carbon balance in the Hawaiian Islands under four unique scenarios over a 90-year timespan. Net ecosystem carbon balance declined under all four scenarios. Moving from a high to a low radiative forcing scenario reduced net ecosystem carbon loss by ~21%, and net carbon losses were reduced by a total of ~55% under the combined scenario of low radiative forcing and low rates of land‐use change. A sensitivity test of the CO~2~ fertilization effect on plant productivity revealed it to be a major source of uncertainty in projections of ecosystem carbon balance. Reconciling this uncertainty in how net photosynthesis will respond to rising atmospheric CO~2~ will be essential to better constrainment of models used to evaluate the effectiveness of ecosystem‐based climate mitigation strategies.

@@

## Methods
We used the Land Use and Carbon Scenario Simulator (LUCAS) to project changes in ecosystem carbon balance for the main Hawaiian Islands under four unique scenarios incorporating different levels of climate and land-use change. The LUCAS model is a state-and-transition simulation model ...
